---
output: github_document
editor_options: 
  markdown: 
    wrap: sentence
---

## Documentation

This README includes: -

-   **Package Overview**: A description of `AutoPrice` and its main features.

-   **Installation Instructions**: How to install the package from GitHub.

-   **Example Usage**: Loading the dataset, conducting basic analysis, and generating summary statistics.

-   **Shiny App Instructions**: How to start and use the Shiny app.

-   **Contributing and License**: Information on contributing to the package and licensing.

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## AutoPrice

<!-- badges: start -->

<!-- badges: end -->

The AutoPrice package provides tools for analyzing vehicle price trends across production years, vehicle makes, models, and more.
This package is designed to support data-driven insights in the automotive industry, focusing on price changes from 2023 to 2025 to help users understand the factors driving price fluctuations.

## Key Features

Dataset Access: A cleaned dataset (vehicles_clean) with over 9,000 vehicles, covering essential details like price, year, make, model, fuel type, mileage, transmission, and body type.
Shiny App: An interactive Shiny app that allows users to explore vehicle price distributions, filter data by various attributes, and download the filtered results.
Data Analysis Tools: Functions for analyzing price trends by production year, vehicle make, and other attributes.

## Installation

You can install the development version of AutoPrice from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# Install devtools if you haven't already
install.packages("devtools")

# Install from GitHub
devtools::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-richisusiljacob")
```

## Getting Started

## Loading the Dataset

The primary dataset, vehicles_clean, can be accessed directly from the package.
This dataset includes vehicles manufactured from 2023 to 2025, with fields such as price, year, make, model, and fuel.

```{r}
library(AutoPrice)

# Load the vehicle price data
data("vehicles_clean")

```

## Basic Analysis Example

Here’s a simple analysis that shows the distribution of vehicle prices by year:

```{r}
library(ggplot2)

ggplot(vehicles_clean, aes(x = year, y = price)) +
  geom_point(alpha = 0.5) +
  labs(title = "Vehicle Price by Production Year",
       x = "Year",
       y = "Price (USD)") +
  theme_minimal()

```

## Summary Statistics

You can also view basic summary statistics of the vehicle prices:

```{r}
summary(vehicles_clean$price)
```

## Shiny App

The AutoPrice package includes a Shiny app for interactive exploration of the dataset.
This app provides tools for filtering vehicle data by year, price range, make, transmission type, and body type.
The app generates a histogram showing the distribution of prices based on these filters, and users can download the filtered data.

## Running the Shiny App

The `AutoPrice` package includes a Shiny app for interactive exploration of the dataset.
This app provides tools for filtering vehicle data by year, price range, make, transmission type, and body type.
The app generates a histogram showing the distribution of prices based on these filters, and users can download the filtered data.

To launch the Shiny app, use the following command:

```{r eval=FALSE}
library(AutoPrice)
VehiclePriceApp()

```

Once the app is running, We can:

-   Filter data by year (2023, 2024, 2025), price range, make, transmission, and body type.

-   View a histogram of vehicle prices based on the selected filters.

-   Download the filtered dataset for further analysis.

## Contributing

We welcome contributions to enhance the functionality of AutoPrice.
If you'd like to contribute, please submit a pull request or open an issue on GitHub.

## License

The AutoPrice package is licensed under the MIT License.

***The full documentation for the `AutoPrice` package is available [here](https://etc5523-2024.github.io/assignment-4-packages-and-shiny-apps-richisusiljacob/).***
