---
title: "AutoPrice"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AutoPrice}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8} 
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r  Warning = FALSE}
library(AutoPrice)
library(dplyr)
library(ggplot2)
library(kableExtra)

```

The AutoPrice package provides a cleaned dataset of vehicle prices, allowing users to explore how factors such as the year, make, and model influence vehicle pricing. This vignette demonstrates the package’s core functionality by analyzing vehicle price trends from 2023 to 2025.

## Loading the Dataset

We’ll start by loading the cleaned dataset vehicles_clean, which contains information on vehicle prices, production years, makes, models, and other specifications.

```{r eval=FALSE}
data("vehicles_clean", package = "AutoPrice")
head(vehicles_clean)

```

## Analyzing Price Trends by Year

To investigate how vehicle prices have changed over time, we’ll plot the average price for each year from 2023 to 2025. This analysis can provide insights into whether newer models command higher prices on average.

```{r Warning = FALSE}
avg_price_by_year <- vehicles_clean %>%
  group_by(year) %>%
  summarise(avg_price = mean(price, na.rm = TRUE))

ggplot(avg_price_by_year, aes(x = year, y = avg_price)) +
  geom_line(color = "steelblue", size = 1.2) +
  geom_point(size = 3) +
  labs(title = "Average Vehicle Price by Year",
       x = "Year",
       y = "Average Price (USD)") +
  theme_minimal()

```

## Exploring Price Distributions by Make

Vehicle prices can vary significantly by make. Let’s examine the distribution of prices for different vehicle manufacturers in 2025 to see which brands tend to be more expensive.

```{r  Warning = FALSE}
ggplot(filter(vehicles_clean, year == 2025), aes(x = make, y = price)) +
  geom_boxplot(fill = "lightblue") +
  labs(title = "Vehicle Price Distribution by Make (2025)",
       x = "Make",
       y = "Price (USD)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## Average Price by Transmission Type

Transmission type (automatic vs. manual) may also affect vehicle prices. Here, we calculate the average price by transmission type to understand if there’s a price premium associated with certain types.

```{r  Warning = FALSE}
avg_price_by_transmission <- vehicles_clean %>%
  group_by(transmission) %>%
  summarise(avg_price = mean(price, na.rm = TRUE))

kableExtra::kable(avg_price_by_transmission) %>%
  kable_styling(font_size = 15)

```

## Using the Shiny App for Interactive Exploration

The `AutoPrice` package includes a Shiny app that provides an interactive way to explore vehicle prices. You can launch the app with the following command:

```{r eval=FALSE}
library(AutoPrice)
AutoPrice::load_shiny_app()
```

This app allows you to:

-   Filter vehicle prices by year, make, transmission type, and body type.

-   View dynamic plots of price distributions.

-   Download filtered data for further analysis.

## Conclusion

This vignette demonstrates some basic analyses you can perform with the AutoPrice package to explore vehicle price trends. By examining trends by year, make, and transmission type, you can gain valuable insights into the factors that influence vehicle prices over time. The Shiny app further enhances the package by allowing for interactive data exploration.

This package offers a flexible and data-driven approach to understanding the automotive market, which can be beneficial for analysts, dealers, and potential buyers.
